s\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{cleveref}
\usepackage{mathptmx} % Times New Roman Font
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{fontawesome5} % For social media icons

\hypersetup{
    colorlinks=true,
    urlcolor=black
}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\setlength{\tabcolsep}{0in}

% Formatting Sections
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r} \textbf{#1} & #2 \\ \textit{\small#3} & \textit{\small #4} \\ \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r} \small#1 & #2 \\ \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%----------- RESUME STARTS HERE -----------

\begin{document}

% Header
\begin{center}
    {{\fontsize{18pt}{22pt} \selectfont \textbf{Amul Poudel}}} \\[3pt]
    \small
    \begin{tabular}{c}
        \faMapMarker\ San Marcos, TX $|$
        \faGithub\ \href{https://github.com/Amul-byte}{Amul-byte} $|$
        \faGlobe\ \href{https://amulpoudel.vercel.app/}{amulpoudel.com.np} $|$
        \faLinkedin\ \href{https://www.linkedin.com/in/amulpoudel/}{amulpoudel} $|$
        \faEnvelope\ \href{mailto:pramulchettri@gmail.com}{pramulchettri@gmail.com} $|$
        \faMobile\ +1 (737) 335 9440
    \end{tabular}
\end{center}

%----------- EDUCATION -----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading{Texas State University}{San Marcos, TX}{Bachelor of Science in Computer Science (GPA: 4.0)}{Expected: May 2028}
\resumeSubHeadingListEnd

%----------- SKILLS -----------
\section{Skills}
\resumeSubHeadingListStart
    \resumeSubItem{\textbf{Languages:} \ Python, HTML, CSS, C/C++, SQL, JavaScript}
    \resumeSubItem{\textbf{Frameworks \& Tools:} \ Django, Git, GitHub, Linux, WordPress, Pandas, Matplotlib, Scikit-Learn, NumPy, MySQL, Streamlit, Tableau }
    \resumeSubItem{\textbf{Data Science / ML:} \ Machine Learning, Data Cleaning, Exploratory Data Analysis, Regression Analysis, Model Evaluation, \newline Data Visualization}
    \resumeSubItem{\textbf{Other Skills:} \ Social Media Handling, Digital Marketing, IT Support, System Administration, Video Editing, Canva, Public Speaking, Time Management}
\resumeSubHeadingListEnd

%----------- EXPERIENCE -----------
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading{Texas State University}{San Marcos, TX}{Assistant to the Director of Facility Management}{Oct 2024 -- Present}
    \resumeItemListStart
        \resumeItem{Managed operations for sports and university events, including baseball, softball, cheer, commencement ceremonies, basketball, football, and soccer.}
        \resumeItem{Developed expertise in logistics, facility operations, and crowd management, ensuring smooth event execution.}
    \resumeItemListEnd

    \resumeSubheading{INKK Engineering Solution Pvt. Ltd.}{Lalitpur, Nepal}{Engineering and 3D Printing Intern}{Oct 2023 -- Feb 2025}
    \resumeItemListStart
        \resumeItem{Researched and implemented FDM 3D printing technologies, optimizing print quality and improving material efficiency.}
        \resumeItem{Managed and maintained 3D printers, troubleshooting hardware issues and ensuring smooth prototyping and production.}
    \resumeItemListEnd

    \resumeSubheading{Waling Innovation Centre}{Syangja, Nepal}{AI and Robotics Club Member}{Feb 2020 -- Feb 2021}
    \resumeItemListStart
        \resumeItem{Developed and implemented AI-driven robotics and automation projects, focusing on real-world machine learning systems.}
        \resumeItem{Researched and optimized robotic motion algorithms, enhancing sensor-based navigation and improving system efficiency.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%----------- PROJECTS -----------
\section{Projects}
\resumeSubHeadingListStart

    % New: ResQMe
    \resumeSubheading{ResQMe — AI-Powered Emergency Response Platform}{Hackathon Project}{Award: SerpApi Community Engagement Winner (\$3{,}000), RiverHacks 2025, {GitHub: \href{https://github.com/gauravfs-14/ResQMe}{ResQMe}}}{2025}
    \resumeItemListStart
        \resumeItem{Co-built an AI platform to streamline emergency reporting and response guidance, focusing on rapid triage and user safety.}
        \resumeItem{Collaborated in a multi-disciplinary team; earned top recognition for community impact and practical utility.}
    \resumeItemListEnd

    % New: Hand Sign Detection
    \resumeSubheading{Hand Sign Detection (ASL A–Z)}{Computer Vision \& Web Application}{Live: \href{https://amulpoudel.streamlit.app/}{amulpoudel.streamlit.app}}{2025}
    \resumeItemListStart
        \resumeItem{Implemented real-time alphabet hand-sign recognition using TensorFlow, OpenCV, and \texttt{cvzone}; supports webcam inference.}
        \resumeItem{Built a responsive Streamlit UI with \texttt{streamlit-webrtc} for low-latency video streaming and seamless user interaction.}
    \resumeItemListEnd

    % New: Interactive Dashboard
    \resumeSubheading{Interactive Census Analytics Dashboard}{Data Visualization Dashboard}{Live: \href{https://dashboard-census.streamlit.app/}{dashboard-census.streamlit.app}}{2025}
    \resumeItemListStart
        \resumeItem{Developed an interactive geospatial dashboard in Plotly Express and Streamlit to explore regional population and literacy\\ trends.}
        \noindent\resumeItem{Added filtering, drill-down tooltips, and map-based visualizations to enable quick, data-driven insights.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%----------- HONORS & AWARDS -----------
\section{Honors \& Awards}
\resumeSubHeadingListStart
    \resumeSubheading{Dean's List - Texas State University}{San Marcos, TX}{Awarded for Academic Excellence (4.0 GPA) $\cdot$ Fall 2024, and Spring 2025}{2024 -- Present}
    \resumeItemListStart
        \resumeItem{Recognized for maintaining a \textbf{4.0 GPA}, demonstrating exceptional academic performance and dedication.}
        \resumeItem{Achieved \textbf{Dean's List distinction} by excelling in coursework and consistently ranking among the top students.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%----------- LANGUAGES -----------
% \section{Languages}
% \resumeSubHeadingListStart
%     \resumeSubItem{English (Fluent), Nepali (Native), Hindi (Fluent)}
% \resumeSubHeadingListEnd

\end{document}
